---
title: Math Geeks + Ryan 
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
  center: true

---

## Age vs Y
```{r echo=FALSE, out.width = "90%"}
setwd("~/Documents/GitHub/OCRugVARKS/data")
data <- read.csv("bank-full.csv", TRUE, ';')
colory <- "#56a8e8"
colorn <- "grey75"  

library(ggplot2)
ggplot(data, aes(age, fill = y)) + geom_bar() +
  theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Age",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
``` 
 
## Percentages of Age vs Y
```{r echo = FALSE, out.width = "90%"}
suppressWarnings(print(ggplot(data, aes(age, fill = y)) + geom_bar(position = "fill") +
  theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Age",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  xlim(18,95) +
  guides(fill = guide_legend(reverse = TRUE))))
```

## Jobs vs Y
```{r}
ggplot(data, aes(job, fill = y)) + coord_flip()  + geom_bar() +
   theme_minimal() + scale_fill_manual(values = c(colorn,colory)) +
  labs(title = NULL, 
  x = "Jobs",
  y = "Number of Persons Called",
  fill = "Subscribed?") +
  guides(fill = guide_legend(reverse = TRUE))
```

## Frequency of Clients Subscribing to a Term Deposit (Age: 18-29)
```{r echo = FALSE, out.width = "90%"}
data_age1 <- data[which(data$age>=18 & data$age <30),]
data_age2 <- data[which(data$age>=30 & data$age <60),]
data_age3 <- data[which(data$age>60),]
ggplot(data_age1, aes(y, fill = y)) + geom_bar() +
  theme_minimal()+
  scale_fill_manual(values = c(colorn,colory)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  geom_text(stat = 'count',aes(label =..count.., vjust = -0.2)) +
  labs(title = NULL,
       x = "Response",
       y = "Frequency",
       fill = "Did the client subscribe a term deposit?")
```

## Frequency of Clients Subscribing to a Term Deposit (Age: 30-59)
```{r echo = FALSE, out.width = "90%"}
ggplot(data_age2, aes(y, fill = y)) + geom_bar() +
  theme_minimal()+
  scale_fill_manual(values = c(colorn,colory)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  geom_text(stat = 'count',aes(label =..count.., vjust = -0.2)) +
  labs(title = NULL,
       x = "Response",
       y = "Frequency",
       fill = "Did the client subscribe a term deposit?")
```

## Frequency of Clients Subscribing to a Term Deposit (Age: 60+)
```{r echo = FALSE, out.width = "90%"}
ggplot(data_age3, aes(y, fill = y)) + geom_bar() +
  theme_minimal()+
  scale_fill_manual(values = c(colorn,colory)) +
  guides(fill = guide_legend(reverse = TRUE)) +
  geom_text(stat = 'count',aes(label =..count.., vjust = -0.2)) +
  labs(title = NULL,
       x = "Response",
       y = "Frequency",
       fill = "Did the client subscribe a term deposit?")
```

## Summary of subsribe bank term by age group
Summary for 'Ages from 18 - 29'

`r summary(data_age1$y)`

17.59 Percent of Age Group 1 subscribed to term deposit

Summary for 'Ages 30-59'

`r summary(data_age2$y)`

9.85 Percent of Age Group 2 subscribed to term deposit

Summary for 'Ages 60+'

`r summary(data_age3$y)`

42.25 Percent of Age Group 3 subscribed to term deposit


## Conclusion 
Out of all Occupations, students had the best ratio 

Age group 1 and Age group 3 were more likely to subscribe

We made assumption that the younger individuals are more likely to subscribe likely and the elderly were thinking about retirement funds



